---
format: gfm
---

<!-- README.md is generated from README.qmd. Please edit that file -->

```{r}
#| label: setup
#| include: false
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  fig.width = 6,
  out.width = "100%",
  fig.retina = 3
)
```

# ggsegMiccai

<!-- badges: start -->
[![R-CMD-check](https://github.com/ggsegverse/ggsegMiccai/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/ggsegverse/ggsegMiccai/actions/workflows/R-CMD-check.yaml)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

MICCAI 2012 Multi-Atlas Labeling brain atlas for the ggseg ecosystem: the maximum
probability tissue labels distributed with SPM12, split into a cortical atlas
(`miccai_cortical()`) and a subcortical atlas
(`miccai_subcortical()`).

## Data licence

The label data were released under the Creative Commons
Attribution-NonCommercial licence (CC BY-NC), so this package is
CC BY-NC 4.0 and may not be used commercially. Credit the MRI scans as
originating from the [OASIS project](https://www.oasis-brains.org/) and the
labeled data as "provided by
[Neuromorphometrics, Inc.](http://Neuromorphometrics.com/) under academic
subscription".

## Atlas Citation

> Landman BA, Warfield SK (Eds.) (2012). *MICCAI 2012 Workshop on
> Multi-Atlas Labeling*.

> Marcus DS, et al. (2007). Open Access Series of Imaging Studies (OASIS):
> cross-sectional MRI data in young, middle aged, nondemented, and demented
> older adults. *Journal of Cognitive Neuroscience*, 19(9), 1498-1507.
> DOI: [10.1162/jocn.2007.19.9.1498](https://doi.org/10.1162/jocn.2007.19.9.1498)

If you use this atlas in your work, please cite both the original atlas publication
and the ggseg package:

> Mowinckel AM, Vidal-Pineiro D (2020). "Visualization of Brain Statistics
> With R Packages ggseg and ggseg3d."
> *Advances in Methods and Practices in Psychological Science*, 3(4), 466-483.
> DOI: [10.1177/2515245920928009](https://doi.org/10.1177/2515245920928009)

## Installation

We recommend installing the ggseg-atlases through the ggsegverse
[r-universe](https://ggsegverse.r-universe.dev/#builds):

```{r}
#| label: install-r-universe
#| eval: false
options(repos = c(
  ggsegverse = "https://ggsegverse.r-universe.dev",
  CRAN = "https://cloud.r-project.org"
))

install.packages("ggsegMiccai")
```

You can install this package from [GitHub](https://github.com/) with:

```r
# install.packages("pak")
pak::pak("ggsegverse/ggsegMiccai")
```

## Usage

```{r}
#| label: cortical
library(ggsegMiccai)

plot(miccai_cortical())
```

```{r}
#| label: subcortical
#| fig-height: 4
plot(miccai_subcortical())
```

## Code of Conduct

Please note that the ggsegMiccai project is released with a
[Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html).
By contributing to this project, you agree to abide by its terms.
